Testing Quasar Unification with Clumpy Wind Models

### 2015-11-10 paper_mnras.tex
bringing up to date with polarisation etc

\begin{table}
\begin{tabular}{p{3cm}p{4cm}}
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
$\alpha_X$ 	 &	 $-0.9$ \\ 
$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$$^*$ \\ 
$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
$\lambda$ 	&	 $0$ \\ 
$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
$\alpha$ 	&	 $0.6^*$ \\
$f$ 	&	 $0.01^*$  \\
\hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
%  $\alpha_{OX} $ 	 &	 -2.2\\ 
\end{tabular}
\caption{Wind geometry parameters used in the model.}
\label{wind_param}
\end{table}

@@

Clumping also causes the total line luminosity to increase dramatically,
as recombination and collisional excitation are both proportional to
$n_e^2$. This line emission typically emerges on the edge of the wind
nearest the central source. The location of the line emitting regions
is dependent on the ionization state, as well as the X-rays heating the plasma.
The radii of these emitting regions is important,
and can be compared to observations. As shown in figure~\ref{fig:wind},
the \civ\ line in our model is typically formed between 
$100-1000~r_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
This is in rough agreement with the reverberation mapping 
results of Kaspi (2000) for the $2.6\times10^{9} M_\odot$ quasar S5 0836+71,
and also compares favourably with microlensing measurements of the size of the
\civ\ emission line region in the BALQSO H1413+117 \citep{odowd2015}.

@@

% \begin{figure*} %fullpage
% \centering
% \includegraphics[width=1.0\textwidth]{figures/opt.png}
% \caption
% {
% Figure designed to show optical spectrum and comparison to composite.
% }
% \label{fig:uvspec}
% \end{figure*} %fullpage

@@

\subsubsection{Broad absorption lines}

@@

The high ionization BAL profiles are often saturated, and the location in velocity space
of the strongest absorption in the profile varies with inclination.
At lower inclinations, the strongest absorption occurs at the red edge,
whereas at high inclinations (and for the strongest BALs)
the trough has a sharp edge at the terminal velocity.
This offers one potential explanation for the wide range of BALQSO absorption
line shapes (see e.g. Trump et al. 2006; Knigge et al 2008).
In addition, the line profile shape is strongly dependent 
on the density, ionization and velocity 
profiles intersected by the line of sight. Thus, small tweaks of the velocity
law and angular distributions of streamlines can dramatically alter
the shape of the line.

@@

\subsubsection{Broad emission lines}

We find that the model can produce significant line emission
at low inclinations, particular in \civ, 
and the improved treatment of recombination results in a strong \la\
line. In the context of unification, this is a promising result, 
and shows that a biconical wind can produce significant 
emission at `quasar-like' angles. 
Our simulated spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
line seen in the quasar composite spectra. This is because we do not yet
treat C as a full macro-atom with a full collisional rates between forbidden
or semi-forbidden transitions, as would be required.
The critical density of the C~\textsc{iii}]~1909\AA\, line 
is $n_e\sim10^{9.5}~\rm{cm^{-3}}$, which is higher than much of the 
outer portion of our wind. We therefore expect a model with these 
parameters to produce C~\textsc{iii}]~1909\AA\ with a proper treament. 
% {\bf we have gone from their being lines we should see, to important coolants.  I think we should stick to the fact that we would think our code would see them if we put C in as a macro atom.  Also I think this who discussion of CIII should be after we have discussed what looks right with the emission lines.}

@@

\subsubsection{The Angular Distribution of Line And Continuum Emission}
\label{discsed}

{\bf: I am not convinced this in the right place in the paper, because here we explore an alternative hypythesis.  It might go better at the end.  But a good many of the following sections are not that well motivated.}

When comparing BALQSO and quasar composites, it is apparent
that they possess remarkably similar line strengths and widths 
\citep[e.g.][]{weymann1991,reichard2003}.  
{\bf I think we mean EW here; otherwise I don't understand what we are talking about.  We could say ``line shapes and equivalent widths''.  I also think this requries more than one sentence of introduction.}
This presents a challenge to our model, as well as the geometric 
unification picture in general, because these quantities should vary with inclination angle.
Limb darkening and foreshortening causes the disc continuum emission to be 
strongly anisotropic, yet the line emission in our models is much more isotropic. 
This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
To construct a scenario where emission 
line equivalent widths are comparable at all inclinations requires 
significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
%An alternative, simpler solution is that the emergent continuum is roughly isotropic.

Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.  Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge. Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated 
\ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
The output flux at three different wavelengths
as a function of inclination for an \agn\ model with the same disc and BH parameters
as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
the effects of GR on an AGN disc are much less extreme 
in the UV portion of the spectrum than the calculations
by \cite{zhang1997} for the X-rays in X-ray binaries.
The emission for the disks of AGN is still strongly anisotropic.
GR alone therefore cannot explain the line ratio trends in quasars by making the disc
emit more isotropically. This supports the findings of \cite{risaliti2011}, 
who find that EW distributions in quasars are consistent with anisotropic emission 
from optically thick, 
disc-like structures for {\em both} the continuum source and BLR. 
If this is the case, it has a dramatic affect on the intrinsic
BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
We will explore these ideas further in a future study.  
{\bf Wait!  All this says is that there has to be an alternative explanation.
It is not support for any specific explanation!. This last few sentences should
be a separate paragraph.  They should start out: An alernative explanation proposed 
by risalite is that...}

@@

\subsection{X-ray Properties and Broadband SEDs}

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/lx.png}
\caption
{
X-ray ($2$~keV) luminosity of the our clumped model (red squares) 
and the H13 model (purple squares), plotted against monochromatic luminosity 
at 2500\AA. The points are labeled according to inclination; angles
$>70^\circ$ correspond to BALs in our scheme (see figure 4).
Also plotted are the samples considered by Saez et al. 2012 on a similar plot; 
The COMBI-7 AGN and the BQS samples Steffen et al. (2006) and the Saez et al. (2012) 
sample of BALQSOs. The dotted line shows the best fit relation for non-BALQSOs 
from Steffen et al. (2006).
}
\label{fig:xray}
\end{figure*} %fullpage

@@

{\bf:  Again this section needs an introduction.  Why is this important?}

Figure~\ref{fig:xray} shows the emergent
monochromatic luminosity ($L_\nu$) at 2~keV and 
%$\alpha_{OX}$ 
plotted against $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
% $\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
% \begin{equation}
% \alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
% \end{equation}
% which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
% weakness. 
The monochromatic luminosities are calculated from the synthetic spectra and thus include
the effects of wind reprocessing and attenuation. In addition to model outputs,
we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
samples from Steffen et al. (2006). The best fit relation from Steffen et al. (2006) 
is also shown. For low inclination, `quasar-like' viewing angles,
we now show excellent agreement with AGN samples. The gradient from $20^\circ$ to
$60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
(resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
is opaque, and thus the X-ray source subtends a smaller solid angle at high inclinations
(resulting in a lower $L_{2keV}$ for higher inclinations).

@@

Our models slightly over-predict the emergent X-ray luminosity at BAL angles, 
although we are limited by poor sample sizes. 
% It is possible that this is due to our wind being overly optically thick to 
% electron scattering at angles which look through the wind. 
If BALQSOs were {\em intrinsically} 
X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
our isotropic assumption foe the X-ray source would be incorrect. 
A polar-biased X-ray source would result in a lower clumping factor being
required in our model. Our specific wind
prescription will also affect the opacities, densities and resultant
ionization structure, which can change the absorption characteristics and resultant
luminosities.
Nevertheless, our input X-ray spectrum
now reproduces the X-ray properties of a luminous quasar as an output,
and at least some BAL angles match the observations.
This satisifies the first-order requirement for the X-ray properties of 
a unified quasar model.

@@

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/c4_angles.png}
\caption
{
\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for wind angles
from $72-79^\circ$. The profiles are plotted relative to the local
continuum with an offset applied for clarity. Lower ionization
profiles appear at a subset of high inclinations, compared
to the ubiquitous \civ\ profile.
}
\label{fig:lobal}
\end{figure*} %fullpage

At certain sightlines, our model now produces blue-shifted BALs in \al\ and \mg --
the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
at the highest inclinations. Line profiles in velocity space 
for \civ, \al\ and \mg, are shown in figure~\ref{fig:lobal} for a range
of BALQSO viewing angles. We find that ionization stratification
of the wind causes lower ionization material has a smaller covering factor, 
as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
This confirms the behaviour expected from a unification model such as Elvis (2000). 
LoBALs are only present at viewing angles close to edge-on ($i>75^\circ$),
as predicted by polarisation results \citep{brotherton1997}.
There is also a correlation between the strength of LoBAL features
and the amount of continuum attenuation at that sightline, particularly
blueward of the Lyman edge as the low ionization base 
intersects the line-of-sight. 
Our model therefore predicts that LoBALQSOs and FeLoBALQSOs 
have stronger Lyman edge absorption and 
be more Compton-thick than HiBALQSOs and Type 1 quasars.
An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
although, as noted in section~\ref{discsed}, BAL fraction 
inferences are fraught with complex selection effects.

@@

\begin{enumerate}
\item We have introduced a first-order treatment 
of clumping in our model, and found that it can now maintain
the required ionization state while agreeing well with the X-ray
properties of AGN/QSOs.
\smallskip
\item We have shown that the degree of ionization stratification
in the model is sufficient that LoBAL line profiles
are seen at a subset of viewing angles, and Fe~\textsc{ii}
absorption is seen at particularly high inclinations.
\smallskip
\item We find that clumping also causes a significant 
increase in the strength of the  emission
lines produced by the model. This is true both
of collisionally excited resonance lines (such as \civ, \nv)
and recombination lines (such as \la, \ha\ and the Balmer series).
\smallskip
\item The line EWs in our models increase with inclination.
BAL and non-BAL quasar composites have comparable EWs, so our model
fails to reproduce this behaviour.
This is due to a fundamental constraint discussed further in section 5. If the BLR
emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
it is simply not possible to achieve line ratios at low inclinations that are comparable to
those at high inclinations. This is a robust conclusion which 
is independent of the assumed BLR geometry and size.
\smallskip
\item We have examined the effect of GR on our disc SED, using the disc atmosphere
and GR ray-tracing code \agn. While including GR effects
does cause the disc SED to become slightly more isotropic,
the effect is not large enough to produce uniform line to continuum ratios
with viewing angle. We briefly discuss other solutions.
\end{enumerate}
Our work confirms a number of expected outcomes from a geometric unification 
model, and suggests that a simple biconical geometry such as this can come close to 
explaining much of the  phenomenology of quasars. Nevertheless, our conclusions pose 
a clear challenge to the current disc wind unification picture.

>>>>

\begin{table}
\begin{tabular}{p{3cm}p{4cm}}
\hline Next-generation Model Parameters 	&	 Value \\ 
\hline \hline 
$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
$\alpha_X$ 	 &	 $-0.9$ \\ 
$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$$^*$ \\ 
$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
$\lambda$ 	&	 $0$ \\ 
$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
$\alpha$ 	&	 $0.6^*$ \\
$f$ 	&	 $0.01^*$  \\
\hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
% $\alpha_{OX} $ 	 &	 -2.2\\ 
\end{tabular}
\caption{Wind geometry parameters used in the model.}
\label{wind_param}
\end{table}

@@

Clumping also causes the total line luminosity to increase dramatically,
as recombination and collisional excitation are both proportional to
density squared. This line emission typically emerges on the edge of the wind
nearest the central source. The location of the line emitting regions
is dependent on the ionization state, as well as the X-rays heating the plasma.
The radii of these emitting regions is important,
and can be compared to observations. As shown in figure~\ref{fig:wind},
the \civ\ line in our model is typically formed between 
$100-1000~r_G$ ($\sim10^{17}-10^{18}~\rm{cm}$).
This is in rough agreement with the reverberation mapping 
results of Kaspi (2000) for the $2.6\times10^{9} M_\odot$ quasar S5 0836+71,
and also compares favourably with microlensing measurements of the size of the
\civ\ emission line region in the BALQSO H1413+117 \citep{odowd2015}.

@@

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/0946.png}
\caption
{
Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
for direct comparison. 
}
\label{fig:stis}
\end{figure*} %fullpage

@@

\subsubsection{Broad absorption lines (`BALQSO-like' angles)}

@@

The high ionization BAL profiles are often saturated, and the location in velocity space
of the strongest absorption in the profile varies with inclination.
At lower inclinations, the strongest absorption occurs at the red edge,
whereas at high inclinations (and for the strongest BALs)
the trough has a sharp edge at the terminal velocity.
This offers one potential explanation for the wide range of BALQSO absorption
line shapes (see e.g. Trump et al. 2006; Knigge et al 2008, Filiz Ak et al. 2014).
In addition, the line profile shape is strongly dependent 
on the density, ionization and velocity 
profiles intersected by the line of sight. Thus, small tweaks of the velocity
law and angular distributions of streamlines can dramatically alter
the shape of the line.

@@

\subsubsection{Broad emission lines (`quasar-like' angles)}

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/ew.png}
\caption
{
Physical properties of the outflow, shown by the coloured contours.
The solid black line marks a sphere at $1000~r_G$.
The dotted lines show the $72^\circ$ and $78^\circ$ sightlines 
to the centre of the system, and illustrate that different sightlines
intersect material of different ionization states.
}
\label{fig:ew}
\end{figure*} %fullpage

We find significant collisionally excited line emission emerges
at low inclinations in the synthetic spectra, particular in the \civ line.
The improved treatment of recombination also results in a strong \la\ line. 
In the context of unification, this is a promising result, 
and shows that a biconical wind can produce significant 
emission at `quasar-like' angles. 
The spectra do not contain the strong C~\textsc{iii}]~1909\AA\, 
line seen in the quasar composite spectra. 
This is because we do not yet treat C as a full macro-atom with a 
full collisional rates between forbidden
or semi-forbidden transitions, as would be required.
The critical density of the C~\textsc{iii}]~1909\AA\, line 
is $n_e\sim10^{9.5}~\rm{cm^{-3}}$ \citep{wei1988}, which is higher than much of the 
outer portion of our wind. 
We therefore expect a model with these 
parameters to produce a C~\textsc{iii}]~1909\AA\ line
with a proper treament.

@@

\subsubsection{The Angular Distribution of Line And Continuum Emission}
\label{angular}

In order to quantitatively assess how emission lines change with 
inclination when blue-shifted absorption 
may affect the line profile, we define the `red wing equivalent width' ($W_{\lambda,RW}$) as
\begin{equation}
W_{\lambda,RW} = \int_{\lambda_0}^{\lambda^\prime} \left( 1 - \frac{F_\lambda}{F_0} \right) d\lambda
\label{rwew}
\end{equation}
where $F_0$ is the continuum flux and the integral is calculated from $\lambda_0$, line centre,
to a wavelength $\lambda^\prime$ where the flux has returned to the continuum level.
This quantity is shown as a function of inclination in figure 5 for the \civ\ and \mg\ UV lines.
We also plot show the $W_{\lambda,RW}$ expected from isotropic line emission and a foreshortened 
and limb darkened disc  as well as $1/2$ equivalent widths from \cite{dipompeo2012b}.

BALQSOs and quasars generally possess very similar emission line properties 
\citep[e.g.][]{weymann1991,reichard2003}. To demonstrate this, we show equivalent width
mean values and standard devaitions from REF in table 3. Clearly, the variation
with inclination in our models is far greater than than the variation 
between quasar to BALQSO samples.  
This presents a challenge to our model, as well as the geometric unification picture in general.
Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
However this effect is small in the UV and optical wavelength regimes, and the 
disc is still anisotropic.

Reprocessing by an extended outflow may also cause a more isotropic
continuum to emerge. Hints that light scattered off a spatially extended 
wind may contribute signiciantly to the emergent continuum come from radiative transfer s
simulations \citep{simproga2012} and microlensing observations \citep{sluse2015}.
However, neither of these examples have sufficient reprocessing efficiencies to 
compensate for the disc anisotropy in this case.
An alternative explanation, suggested by \cite{risaliti2011}, is that
the BLR has the same angular distribution of emission as the accretion disc.
They find that EW distributions in quasars are consistent with anisotropic emission 
from optically thick, disc-like structures for {\em both} the continuum source and BLR. 
If this is the case, it has a dramatic affect on the intrinsic
BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.

The final possibility is that BALQSOs are not viewed equatorially. 
This possibility is supported by measurements of the radio spectral indices
of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
viewed from a fairly narrow range of angles ($0$-$50^\circ$, and could also mean 
the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
There is also clear conflict between this explanation and some
polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).

% When comparing BALQSO and quasar composites, it is apparent
% that they possess remarkably similar line strengths and widths 
% \citep[e.g.][]{weymann1991,reichard2003}.  
% {\bf I think we mean EW here; otherwise I don't understand what we are talking about.  We could say ``line shapes and equivalent widths''.  I also think this requries more than one sentence of introduction.} This presents a challenge to our model, as well as the geometric 
% unification picture in general, because these quantities should vary with inclination angle.
% Limb darkening and foreshortening causes the disc continuum emission to be 
% strongly anisotropic, yet the line emission in our models is much more isotropic. 
% This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
% To construct a scenario where emission 
% line equivalent widths are comparable at all inclinations requires 
% significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
%An alternative, simpler solution is that the emergent continuum is roughly isotropic.

% Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
% General relativistic effects -- specifically, light bending
% and relativistic beaming -- can cause 
% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.  Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge. Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated 
% \ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
% The output flux at three different wavelengths
% as a function of inclination for an \agn\ model with the same disc and BH parameters
% as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
% the effects of GR on an AGN disc are much less extreme 
% in the UV portion of the spectrum than the calculations
% by \cite{zhang1997} for the X-rays in X-ray binaries.
% The emission for the disks of AGN is still strongly anisotropic.
% GR alone therefore cannot explain the line ratio trends in quasars by making the disc
% emit more isotropically. This supports the findings of \cite{risaliti2011}, 
% who find that EW distributions in quasars are consistent with anisotropic emission 
% from optically thick, 
% disc-like structures for {\em both} the continuum source and BLR. 
% If this is the case, it has a dramatic affect on the intrinsic
% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
% We will explore these ideas further in a future study.  
% {\bf Wait!  All this says is that there has to be an alternative explanation.
% It is not support for any specific explanation!. This last few sentences should
% be a separate paragraph.  They should start out: An alernative explanation proposed 
% by risalite is that...}

@@

\subsection{X-ray Properties and Broadband SEDs}
\label{sec:xray}

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/lx_a05_pre.png}
\caption
{
X-ray ($2$~keV) luminosity of the our clumped model (red squares) 
and the H13 model (purple squares), plotted against monochromatic luminosity 
at 2500\AA. The points are labeled according to inclination; angles
$>70^\circ$ correspond to BALs in our scheme (see figure 4).
Also plotted are the samples considered by Saez et al. 2012 on a similar plot; 
The COMBI-7 AGN and the BQS samples Steffen et al. (2006) and the Saez et al. (2012) 
sample of BALQSOs. The dotted line shows the best fit relation for non-BALQSOs 
from Steffen et al. (2006).
}
\label{fig:xray}
\end{figure*} %fullpage

@@

%{\bf:  Again this section needs an introduction.  Why is this important?}

One of the main motivations for including a treatment of clumping was
to avoid over-ionization of the wind in the presence of strong X-rays. 
Having verified that strong BALs appear in the synthetic spectra,
it is also important to assess whether the X-ray properties of this
next-generation model agree well with quasar and BALQSO samples for the relevant
inclinations.

Figure~\ref{fig:xray} shows the emergent
monochromatic luminosity ($L_\nu$) at 2~keV and 
%$\alpha_{OX}$ 
plotted against $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
% $\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
% \begin{equation}
% \alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
% \end{equation}
% which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
% weakness. 
The monochromatic luminosities are calculated from the synthetic spectra and thus include
the effects of wind reprocessing and attenuation. In addition to model outputs,
we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
samples from Steffen et al. (2006). The best fit relation from Steffen et al. (2006) 
is also shown. For low inclination, `quasar-like' viewing angles,
we now find excellent agreement with AGN samples. The gradient from $20^\circ$ to
$60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
(resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
is opaque, and thus the X-ray source subtends a smaller solid angle at high inclinations
(resulting in a lower $L_{2keV}$ for higher inclinations).

@@

Our models slightly over-predict the emergent X-ray luminosity at BAL angles, 
although we are limited by poor sample sizes. 
% It is possible that this is due to our wind being overly optically thick to 
% electron scattering at angles which look through the wind. 
If BALQSOs were {\em intrinsically} 
X-ray weak \citep[as suggested by, e.g.][]{morabito2013},
our isotropic assumption for the X-ray source would be incorrect. 
A polar-biased X-ray source would result in a lower clumping factor being
required in our model. Our specific wind
prescription will also affect the opacities, densities and resultant
ionization structure, which can change the absorption characteristics and resultant
luminosities.
Nevertheless, our input X-ray spectrum
now reproduces the X-ray properties of a luminous quasar as an output,
and at least some BAL angles match the observations.
This satisifies the first-order requirement for the X-ray properties of 
a unified quasar model.

@@

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/c4_angles.png}
\caption
{
\civ , \mg , \al\ and Fe~\textsc{ii} line profiles for viewing angles
from $72-79^\circ$. The profiles are plotted relative to the local
continuum with an offset applied for clarity. Lower ionization
profiles appear at a subset of high inclinations, compared
to the ubiquitous \civ\ profile.
}
\label{fig:lobal}
\end{figure*} %fullpage

At certain sightlines, the synthetic spectra exhibit blue-shifted BALs in \al\ and \mg --
the absorption lines seen in LoBALQSOs, and we even see absorption in Fe~\textsc{ii}
at the highest inclinations. Line profiles in velocity space 
for \civ, \al\ and \mg, are shown in figure~\ref{fig:lobal} for a range
of BALQSO viewing angles. We find that ionization stratification
of the wind causes lower ionization material to have a smaller covering factor, 
as demonstrated by figures~\ref{fig:wind} and \ref{fig:lobal}.
This confirms the behaviour expected from a unification model such as Elvis (2000). 
LoBALs are only present at viewing angles close to edge-on ($i>75^\circ$),
as predicted by polarisation results \citep{brotherton1997}.
As observed in a BALQSO sample by \cite{filizak2014}, we find that
BAL troughs are wider and deeper when lower ionization species are present,
and high ionization lines have higher blue-edge velocities than the 
lower ionization species.
There is also a correlation between the strength of LoBAL features
and the amount of continuum attenuation at that sightline, particularly
blueward of the Lyman edge as the low ionization base 
intersects the line-of-sight. 
A model such as this therefore predicts that LoBALQSOs and FeLoBALQSOs 
have stronger Lyman edge absorption and 
are more Compton-thick than HiBALQSOs and Type 1 quasars.
An edge-on scenario also offers a potential explanation for the rarity of LoBAL and
FeLoBAL quasars, due to a foreshortened and attenuated continuum, 
although, as noted in section~\ref{discsed}, BAL fraction 
inferences are fraught with complex selection effects.

@@

\begin{enumerate}
\item We have introduced a first-order treatment 
of clumping in our model, and found that it can now maintain
the required ionization state while agreeing well with the X-ray
properties of AGN/QSOs.
\smallskip
\item We have shown that the degree of ionization stratification
in the model is sufficient that LoBAL line profiles
are seen at a subset of viewing angles, and Fe~\textsc{ii}
absorption is seen at particularly high inclinations.
\smallskip
\item We find that clumping also causes a significant 
increase in the strength of the  emission
lines produced by the model. This is true both
of collisionally excited resonance lines (such as \civ, \nv)
and recombination lines (such as \la, \ha\ and the Balmer series).
\smallskip
\item The line EWs in our models increase with inclination.
BAL and non-BAL quasar composites have comparable EWs, so our model
fails to reproduce this behaviour.
This is due to a fundamental constraint discussed further in section 5. If the BLR
emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
it is simply not possible to achieve line ratios at low inclinations that are comparable to
those at high inclinations. This is a robust conclusion which 
is independent of the assumed BLR geometry and size.
% \smallskip
% \item We have examined the effect of GR on our disc SED, using the disc atmosphere
% and GR ray-tracing code \agn. While including GR effects
% does cause the disc SED to become slightly more isotropic,
% the effect is not large enough to produce uniform line to continuum ratios
% with viewing angle. We briefly discuss other solutions.
\end{enumerate}
Our work confirms a number of expected outcomes from a geometric unification 
model, and suggests that a simple biconical geometry such as this can come close to 
explaining much of the  phenomenology of quasars. Nevertheless, our conclusions pose 
a clear challenge to the current disc wind unification picture.

% To resolve these challenges, we suggest the following routes forward.
% \begin{enumerate}
% \smallskip
% \item 
% \smallskip
% \item 
% \smallskip
% \item It is clear that the commonly accepted paradigm of an equatorial
% wind with a covering factor of $\sim20\%$ does provide an adequate 
% unified model, as shown here and by other authors 
% (e.g. Marin \& Goosman 2013; DiPompeo et al. 2012a).
% More collimated winds may solve some problems, but must be reconciled with
% polarisation results that suggest an equatorial geometry.
% Computing the polarisation of emergent energy packets in our 
% MCRT code would allow direct comparison
% between outputs from a known geometry and 
% spectropolarimetry of quasars and AGN.
% \smallskip
% \item In addition to spectropolarimetry, one
% of the best observational tools for probing outflow geometries
% is reverberation mapping. We are starting to 
% incorporate methods for predicting the reverberation
% outputs from our models. By comparing with observational data, this
% may provide stronger constraints on outflow geometries.
% \end{enumerate}
